A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-07 paper.tex
one chief import to should be considered

The goals of any harmonization exercise is threefold: aligning model results in
the harmonization year to a common historical data source, faithfully
representing the original \gls{iam}’s internal consistency between the driver of
emissions (e.g. energy use) and emissions, and maintaining critical parameters
from the original scenario design. Any harmonization method achieves the first
goal by design. If the difference between the model base year and historical
values are small, considering the second and third goals leads to a method
choice that matches modeled drivers (e.g., a \code{ratio} method discussed in
Section \ref{sec:harm-methods}) and converges prior to the final model year. It
preserves the relationship between \gls{iam} output and emissions inventory in
the base year while also matching the original model output at some point in the
modeled time period. It furthermore maintains the consistency of the model's
usage of energy technology, volume of agricultural activities, and abatement
options with harmonized emissions trajectory.

@@

Separately, if there are large discrepancies between the model results in the
base year and the historic data used for harmonization, convergence methods can
result in harmonized trajectories that do not faithfully represent the
underlying drivers of emissions. Furthermore, if models report negative
emissions, as is possible in scenarios designed to depict the deployment of
climate mitigation policies with large \cotwo reductions and storage,
then end-of-century emissions characteristics can be of chief import in order to
faithfully match the design parameters of the original scenarios, such as global
mean temperature and other climate metrics.

@@

This work presented a novel methodology and Python implementation of automated
emissions harmonization for \glspl{iam}, \code{aneris}. An in-depth explanation
of the processes and methods for determining the use of harmonization methods
was provided in Section \ref{sec:meths}. \code{aneris} was able to
satisfactorily harmonized over 96\% of the 1940 individual trajectories that
were analyzed in Section \ref{sec:results}. Of the remaining trajectories,
harmonization method overrides were applied, and  discussion was provided
detailing why overrides were deemed necessary.

>>>>

The goals of any harmonization exercise are threefold: aligning model results in
the harmonization year to a common historical data source, faithfully
representing the original \gls{iam}’s internal consistency between the driver of
emissions (e.g. energy use) and emissions, and maintaining critical parameters
from the original scenario design. Any harmonization method achieves the first
goal by design. If the difference between the model base year and historical
values are small, considering the second and third goals leads to a method
choice that matches modeled drivers (e.g., a \code{ratio} method discussed in
Section \ref{sec:harm-methods}) and converges prior to the final model year. It
preserves the relationship between \gls{iam} output and emissions inventory in
the base year while also matching the original model output at some point in the
modeled time period. It furthermore maintains the consistency of the model's
usage of energy technology, volume of agricultural activities, and abatement
options with harmonized emissions trajectory.

@@

Separately, if there are large discrepancies between the model results in the
base year and the historic data used for harmonization, convergence methods can
result in harmonized trajectories that do not faithfully represent the
underlying drivers of emissions. Furthermore, if models report negative
emissions, as is possible in scenarios designed to depict the deployment of
climate mitigation policies with large \cotwo reductions and storage, then
end-of-century emissions characteristics should be considered in order to
faithfully match the design parameters of the original scenarios, such as global
mean temperature and other climate metrics.

@@

This work presented a novel methodology and Python implementation of automated
emissions harmonization for \glspl{iam}, \code{aneris}. An in-depth explanation
of the processes and methods for determining the use of harmonization methods
was provided in Section \ref{sec:meths}. \code{aneris} was able to
satisfactorily harmonize over 96\% of the 1940 individual trajectories that
were analyzed in Section \ref{sec:results}. Of the remaining trajectories,
harmonization method overrides were applied, and  discussion was provided
detailing why overrides were deemed necessary.
